### 2021-01-25 README.Rmd
edited fit_one_fold() output to be complete focal_vs_comp data frame itself, not just y_hat

```{r}
ex_bw <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, cv_grid = cv_grid_sf_ex) %>%
  right_join(growth_ex, by = c("focal_ID" = "ID"))
```

@@

```{r}
ex_bw %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

>>>>

```{r}
focal_vs_comp_ex <- focal_vs_comp_ex %>%
  run_cv(comp_dist = comp_dist, cv_grid = cv_grid_sf_ex)
```

@@
